%% Pedro Serio - CV
%% Cloud Solutions Architect | Bioinformatics Infrastructure Engineer
%% Master reference CV with all competencies, experience, and achievements.
%% Use as source when building targeted CVs.
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Pedro Serio - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.77]{geometry}
\usepackage{import}

% personal data
\name{Pedro}{Serio}
\address{S\~{a}o Paulo, Brazil}{}{}
\phone[mobile]{+55 11 99999-9999}
\email{pedroaserio@gmail.com}
\extrainfo{\href{https://linkedin.com/in/pedro-serio}{LinkedIn}, \href{https://github.com/pedro-serio}{GitHub}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Results-driven Cloud Solutions Architect and Bioinformatics Infrastructure Engineer with over 5 years of experience architecting, scaling, and automating production-grade, high-throughput data pipelines and event-driven cloud systems. AWS Certified Solutions Architect with deep expertise in Python backend development, AWS Cloud Architecture, and translating complex, data-intensive workflows into reliable, distributed microservices. Combines strong computational infrastructure skills with domain expertise in genomics, oncology, and precision medicine.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Cloud Architecture \& Infrastructure}: AWS (Lambda, ECS, S3, EC2, Batch, DynamoDB, SNS, SQS, IAM, DataSync, CDK), Serverless Architecture, Event-Driven Systems, Microservices, Hybrid Cloud (On-Premises + AWS)

\item \textbf{Backend \& Automation}: Python (Advanced), Bash/Shell Scripting, Linux/Unix Operations, CI/CD Pipeline Automation, Clean Code Principles, Defensive Design Patterns

\item \textbf{Data Pipelines \& Orchestration}: Nextflow, WDL, High-Throughput Processing, Automated Bioinformatics Pipelines, Large-Scale Data Infrastructure

\item \textbf{Bioinformatics \& Genomics}: NGS Analysis, Variant Calling (Illumina DRAGEN), Translational Research, Precision Medicine, Oncogenomics, Variant Interpretation Platforms (Emedgene, Franklin, Varstation)

\item \textbf{Platform \& Tooling}: LIMS Integration, Data Version Control (Git), NoSQL (DynamoDB), VS Code, Illumina Platforms (iSeq, NextSeq, NovaSeq 6000, NovaSeq X+)

\end{itemize}

% ============================================================
%     CERTIFICATIONS
% ============================================================

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item{\textbf{AWS Certified Solutions Architect -- Associate} (SAA-C03), Amazon Web Services, 2025}
\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Genesis Genomics R&D ---
\item{\cventry{2025--Present}{Cloud Infrastructure \& Automation Engineer (R\&D Team)}{Genesis Genomics}{S\~{a}o Paulo, Brazil}{}{\vspace{1pt}
\begin{itemize}
    \item Architect, deploy, and validate highly scalable, cloud-native (AWS) and hybrid on-premises automation platforms, applying robust distributed computing patterns to handle multi-terabyte genomic datasets.
    \item Engineer and maintain custom analytical microservices and Python-based internal toolkits, leveraging serverless cloud triggers (Lambda, SNS, SQS) to streamline background execution and data ingestion flows.
    \item Implement and validate bioinformatics pipelines (Illumina DRAGEN) across cloud and on-premises infrastructure, reducing variant calling time from hours to minutes.
    \item Apply Clean Code principles and defensive design patterns to complex production data pipelines, optimizing execution runtime, system maintainability, and pipeline reliability.
\end{itemize}}}

\vspace{3pt}

% --- Genesis Genomics Operations ---
\item{\cventry{2024--2025}{Cloud Systems \& Operations Analyst (Operational Team)}{Genesis Genomics}{S\~{a}o Paulo, Brazil}{}{\vspace{1pt}
\begin{itemize}
    \item Provided critical tier support, performance tuning, and incident troubleshooting for high-throughput data servers and infrastructure platforms under strict operational SLAs.
    \item Managed daily AWS cloud environment operations (S3, IAM, DataSync, Lambda, CLI), ensuring stringent data security compliance, identity and access management, and optimized asset transfer workflows.
    \item Led technical cross-functional initiatives to integrate internal laboratory information management systems (LIMS) with platform APIs, automating end-to-end service order data synchronization.
    \item Administered variant analysis platforms (Emedgene, Franklin, Varstation) and operated Illumina sequencers (iSeq, NextSeq, NovaSeq 6000, NovaSeq X+) with 99.9\% uptime.
\end{itemize}}}

\vspace{3pt}

% --- Grupo Fleury ---
\item{\cventry{2023--2024}{Systems \& Data Analyst}{Grupo Fleury -- Genomics Center}{S\~{a}o Paulo, Brazil}{}{\vspace{1pt}
\begin{itemize}
    \item Managed and optimized technical data workflows, ensuring quality control across large-scale sample inputs and computational data processing.
    \item Developed and maintained analytical tools for genomic data processing and quality assurance.
\end{itemize}}}

\vspace{3pt}

% --- PhD ---
\item{\cventry{2018--2023}{PhD Scientist \& Data Developer}{Oncology Translational Research Center (CTO/ICESP)}{S\~{a}o Paulo, Brazil}{}{\vspace{1pt}
\begin{itemize}
    \item Developed custom scripts (Python/R) for large-scale oncogenomics data analysis, handling complex databases and extracting actionable insights for precision medicine.
    \item Performed NGS sequencing, bioinformatics analysis, and statistical interpretation for translational oncology research.
    \item Mentored junior researchers and led training initiatives in bioinformatics and molecular oncology.
\end{itemize}}}

\vspace{3pt}

% --- UNIFESP ---
\item{\cventry{2014--2016}{Laboratory Assistant}{Federal University of S\~{a}o Paulo (UNIFESP)}{S\~{a}o Paulo, Brazil}{}{\vspace{1pt}
\begin{itemize}
    \item Supported molecular biology research projects, gaining foundational experience in laboratory techniques and data management.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{2023--2025}{MBA in Data Science and Analytics}{ESALQ/USP}{S\~{a}o Paulo, Brazil}{}{\vspace{1pt}
Data science, analytics, machine learning, and business intelligence.
}}

\vspace{3pt}

\item{\cventry{2018--2023}{PhD in Genomics and Transcriptomics in Oncology}{FMUSP/ICESP}{S\~{a}o Paulo, Brazil}{}{\vspace{1pt}
Thesis: ``Somatic Mutational Profiling and Computational Analysis in Oncogenomics.'' Focus on data-driven mutational profiling and computational analysis for precision medicine.
}}

\vspace{3pt}

\item{\cventry{2017--2018}{Specialization in Cancer Molecular Biology}{FMUSP/ICESP}{S\~{a}o Paulo, Brazil}{}{\vspace{1pt}
Cancer biology, molecular techniques, and translational research methods.
}}

\vspace{3pt}

\item{\cventry{2012--2016}{Bachelor's Degree in Biomedical Science (Molecular Biology)}{UNIP}{S\~{a}o Paulo, Brazil}{}{\vspace{1pt}
Molecular biology, cell biology, and biomedical sciences.
}}

\end{itemize}

% ============================================================
%     PROFESSIONAL TRAINING
% ============================================================

\section{Professional Training}
\vspace{1pt}
\begin{itemize}
\item Architecting on AWS -- Fast Lane (2025)
\item Data Science in Python -- Michigan State University (2022)
\item Bioinformatic Methods (Data Processing) -- University of Toronto (2021)
\end{itemize}

% ============================================================
%     TEACHING \& LEADERSHIP
% ============================================================

\section{Teaching \& Leadership}
\vspace{1pt}
\begin{itemize}
\item{\textbf{VI Course in Molecular Oncology} -- ICESP (2021): Organizing Committee Member and Lecturer. Introduced genomics, data structures, and bioinformatics concepts to researchers.
}
\end{itemize}

% ============================================================
%     PUBLICATIONS
% ============================================================

\section{Selected Publications}
\vspace{1pt}
\begin{itemize}
\item Rodrigues LM et al. (2024). Prevalence of germline variants in Brazilian pancreatic carcinoma patients. \textit{Scientific Reports} (Nature).
\item Serio PAMP et al. (2021). Somatic Mutational Profile of High-Grade Serous Ovarian Carcinoma and Triple-Negative Breast Carcinoma in Young and Elderly Patients. \textit{Cells}.
\item Katayama MLH et al. (2019). Stromal Cell Signature Associated with Response to Neoadjuvant Chemotherapy in Locally Advanced Breast Cancer. \textit{Cells}.
\item Encinas G et al. (2018). Somatic Mutations in Early-Onset Luminal Breast Cancer. \textit{Oncotarget}.
\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Portuguese (native), English (fluent), Spanish (basic).
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
